---
title: "Assignment 1"
author: "Christina Chang"
date: "2/9/2018"
output: html_document
---

# 1. NYC flights
```{r}
library(nycflights13) # load package
```

## a. How many variables and observations does the data.frame "flights" from the nycflights13 package contain? 
```{r}
ncol(flights) # variables

nrow(flights) # observations
```

## b. Select the flights that started from NYC at the first day of each month! 
```{r, message=FALSE}
library(dplyr) # to manipulate data

flights_sub <- filter(flights, 
                      origin == c("LGA","JFK"), # EWR is technically outside NYC
                      day == 1)
```

## c. Sort flights by time of arrival! 
```{r}
flights_sub <- arrange(flights, desc(arr_time))
```

## d. How many flights started from all the NYC airports in 2013? 
```{r}
flights %>%  
  filter(origin == c("LGA","JFK"), # again EWR not included (see above reasoning)
         year == 2013) %>%
  nrow()
```

## e. Which carrier had the biggest mean net delay (departure delay minus arrival delay), which the lowest? 
```{r}
flights <- mutate(flights, net_delay = dep_delay + arr_delay)

flights_by_carrier <- group_by(flights, carrier)

summarize(flights_by_carrier, net_delay = mean(net_delay, na.rm = TRUE))
```
### F9 is the carrier with biggest mean net delay
### AS is the carrier with lowest mean net delay

## f. Inspect visually how the net delays are distributed!
```{r}
hist(flights$net_delay, 
     main="Histogram of Net Delay",
     xlab="Net Delay",
     col="red")
```

# 2. Baby names
```{r}
library(babynames)
```

## a. Which time period does the data frame cover? 
```{r}
str(babynames)
summary(babynames$year)
```
### From 1880 to 2015. 

## b. What has been the most frequent name in the US since 1880? 
```{r}
babynames2 <- babynames %>% 
  group_by(name) %>% 
  summarise(nrow = length(name)) %>% 
  arrange(desc(nrow))

head(babynames2)

babynames2[babynames2$nrow==272, "name"]
```

## c. Use graphical means to determine since which year the name "Kim" became more popular as a female than a male name! 
```{r}
female_Kim <- babynames %>% 
  filter(sex == "F", name == "Kim")

plot(female_Kim$year, female_Kim$n, type="l",col="green")

male_Kim <- babynames %>%
  filter(sex == "M", name == "Kim")

lines(male_Kim$year, male_Kim$n,col="red")


```

### It looks like 1955 is the year that "Kim" became more popular as a female than a male name. 